---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: cosmo
---


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(readr)
library(highcharter)
library(dplyr)
#Prepare the data for visualization

CustomerData = read.csv("Online Retail.csv", stringsAsFactors = TRUE)
names(CustomerData)[1] = "InvoiceNo"

#Create a new column called Total cost
CustomerData$Cost = CustomerData$UnitPrice * CustomerData$Quantity

#convert date columns
library(lubridate)

#Work on the date column to have Month and Season
CustomerData$InvoiceDate = dmy_hm(CustomerData$InvoiceDate)
CustomerData$hour = format(as.POSIXct(CustomerData$InvoiceDate,format="%H:%M:%S"),"%H")
CustomerData$MoSold = format(as.POSIXct(CustomerData$InvoiceDate,format="%y:%m:%d"),"%m")
CustomerData$MoSold = as.numeric(CustomerData$MoSold)
#season
CustomerData$seasons = ifelse(CustomerData$MoSold == 3|CustomerData$MoSold == 4 |CustomerData$MoSold == 5,"Spring",
                  ifelse( CustomerData$MoSold == 6|CustomerData$MoSold == 7 |CustomerData$MoSold == 8,"Summer",
                    ifelse(CustomerData$MoSold == 9|CustomerData$MoSold == 10 |CustomerData$MoSold == 11,"Autumn",
                         ifelse(CustomerData$MoSold == 12|CustomerData$MoSold == 01 |CustomerData$MoSold == 2,"Winter",0))))

CustomerData$Quantity[CustomerData$Quantity <= 0] = NA
CustomerData$UnitPrice[CustomerData$UnitPrice <= 0]= NA


#Make factor mosold seasons and hour
CustomerData[,c(10:12)] <- lapply(CustomerData[,c(10:12)], factor)

#where are the Missing values
library(VIM)

 
Missness = data.frame(colMeans(is.na(CustomerData))) #only customerID is missing and theres no way to get it so we can represent them as 00000
x = CustomerData
y = CustomerData
x$CustomerID[is.na(x$CustomerID)] = "00000" 
x$CustomerID = as.factor(x$CustomerID)

#remove other
x = na.omit(x)

#create sentiment score
x$Sentiment_score = sample(c(2,4,6,8,10),530104,rep = TRUE,prob = c(0.01, 0.04, 0.04,0.04,0.87))

#create rfm score of each customer
#install.packages("rfm")
library(dplyr)
#remove all data with 00000
y = na.omit(y)
y$order_date = as_date(y$InvoiceDate, tz = "UTC") 
analysis_date = as_date("2012-01-01", tz = "UTC")
df_RFM = y %>%
      group_by(CustomerID) %>%
      summarise(Recency = as.numeric(analysis_date - max(order_date)), Frequency = n_distinct(InvoiceNo), Monetary_Value = round (sum(Cost),2))

#bring country of each customer
x3 = match(df_RFM$CustomerID,y$CustomerID)
ix3= y[x3,]
df_RFM$Country = ix3$Country

df_RFM = df_RFM[-1,]

#create a score for each of the customers
#R_score
df_RFM$R_Score = NA
df_RFM$R_Score[df_RFM$Recency>164.8]<-1
df_RFM$R_Score[df_RFM$Recency>73 & df_RFM$Recency<=164.8 ]<-2
df_RFM$R_Score[df_RFM$Recency>40 & df_RFM$Recency<=73 ]<-3
df_RFM$R_Score[df_RFM$Recency<=40]<-4

#F_score
df_RFM$F_Score = NA
df_RFM$F_Score[df_RFM$Frequency<1]<-1
df_RFM$F_Score[df_RFM$Frequency>=1 & df_RFM$Frequency<2]<-2
df_RFM$F_Score[df_RFM$Frequency>=2 & df_RFM$Frequency<5 ]<-3
df_RFM$F_Score[df_RFM$Frequency>=5]<-4

#M_score
df_RFM$M_Score = NA
df_RFM$M_Score[df_RFM$Monetary_Value<= 307.42]<-1
df_RFM$M_Score[df_RFM$Monetary_Value>=307.42 & df_RFM$Monetary_Value<674.49]<-2
df_RFM$M_Score[df_RFM$Monetary_Value>=674.49 & df_RFM$Monetary_Value<1661.74 ]<-3
df_RFM$M_Score[df_RFM$Monetary_Value>=1661.74]<-4

#RFM_score
df_RFM<- df_RFM %>% mutate(RFM_Score = 100*R_Score + 10*F_Score+M_Score)

#classify them into segments
df_RFM$segmentRFM<- ifelse(df_RFM$RFM_Score == 444, "Champions",
                           ifelse(df_RFM$RFM_Score == 334 |df_RFM$RFM_Score == 342 |df_RFM$RFM_Score == 343 |df_RFM$RFM_Score == 344 |df_RFM$RFM_Score == 433 |df_RFM$RFM_Score == 434 |df_RFM$RFM_Score == 443,"Loyal_Customers",
                                  ifelse(df_RFM$RFM_Score == 332 |df_RFM$RFM_Score == 333 |df_RFM$RFM_Score == 341 |df_RFM$RFM_Score == 412 |df_RFM$RFM_Score == 413 |df_RFM$RFM_Score == 414 |df_RFM$RFM_Score == 431|df_RFM$RFM_Score == 432 |df_RFM$RFM_Score == 441 |df_RFM$RFM_Score == 442 |df_RFM$RFM_Score == 421|df_RFM$RFM_Score == 422 |df_RFM$RFM_Score == 423 |df_RFM$RFM_Score == 424,"Potential_Loyalist",
                                         ifelse(df_RFM$RFM_Score == 411, "Recent_Customers",
                                                ifelse(df_RFM$RFM_Score == 311 |df_RFM$RFM_Score == 312 |df_RFM$RFM_Score == 313 |df_RFM$RFM_Score == 331,"Promising",
                                                       ifelse(df_RFM$RFM_Score == 212 |df_RFM$RFM_Score == 213 |df_RFM$RFM_Score == 214 |df_RFM$RFM_Score == 231 |df_RFM$RFM_Score == 232 |df_RFM$RFM_Score == 233 |df_RFM$RFM_Score == 241|df_RFM$RFM_Score == 314 |df_RFM$RFM_Score == 321 |df_RFM$RFM_Score == 322 |df_RFM$RFM_Score == 323|df_RFM$RFM_Score == 324,"Needing_Attention",
                                                              ifelse(df_RFM$RFM_Score == 211,"About_to_Sleep",
                                                                     ifelse(df_RFM$RFM_Score == 112 |df_RFM$RFM_Score == 113 |df_RFM$RFM_Score == 114 |df_RFM$RFM_Score == 131 |df_RFM$RFM_Score == 132 |df_RFM$RFM_Score == 133 |df_RFM$RFM_Score == 142|df_RFM$RFM_Score == 124 |df_RFM$RFM_Score == 123 |df_RFM$RFM_Score == 122 |df_RFM$RFM_Score == 121|df_RFM$RFM_Score == 224|df_RFM$RFM_Score == 223 |df_RFM$RFM_Score == 222 |df_RFM$RFM_Score == 221,"At_Risk",
                                                                            ifelse(df_RFM$RFM_Score == 134 |df_RFM$RFM_Score == 143 |df_RFM$RFM_Score == 144 |df_RFM$RFM_Score == 234 |df_RFM$RFM_Score == 242 |df_RFM$RFM_Score == 243 |df_RFM$RFM_Score == 244,"Can't_Lose",
                                                                                   ifelse(df_RFM$RFM_Score == 141,"Hibernating",
                                                                                          ifelse(df_RFM$RFM_Score == 111,"Lost","UN")))))))))))


#check the amount earned in each country
df1 = x %>%
  group_by(Country) %>%
summarise(Amount = sum(Cost))

#arrange df1  
df1 = df1 %>%
  arrange(desc(Amount))

```

Overview {data-orientation=rows data-icon="fa-bar-chart"}
=====================================

## Row 1 {data-height=110}

### Number of Customers

```{r}
valueBox(4373, icon = "fa-ship", color="rgb(100,100,100)")
```

### Number of Countries

```{r}
valueBox(37, icon = "fa-heart", color="rgb(200,100,100)")
```

### Turnover

```{r}
valueBox("$9.7M", icon = "fa-life-ring",color="rgb(26,110,204)")
```
    

## Row 2 {data-height=400}  

### Sales over the years
    
```{r}
# Libraries
library(ggplot2)
library(dplyr)
library(plotly)
library(hrbrthemes)


# Load dataset from github
salesday = x[,c("InvoiceDate","Cost")]
salesday$InvoiceDate = as.Date(salesday$InvoiceDate)
salesday = salesday %>%
  group_by(InvoiceDate) %>% 
  summarise(Cost = sum(Cost))

# Usual area chart
p <- salesday %>%
  ggplot( aes(x=InvoiceDate, y=Cost)) +
    geom_area(fill="#69b3a2", alpha=0.5) +
    geom_line(color="#69b3a2") +
    ylab("Sales") +
    theme_ipsum()

# Turn it interactive with ggplotly
p <- ggplotly(p)
p

```
    

## Row 3 {data-height=400}  

### Sales by Country

```{r}
dfC <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv')
dfC$GDP..BILLIONS.= NULL

xMap = x
xMap$Country[xMap$Country == "Unspecified"] = NA
xMap = na.omit(xMap)

x5 = match(xMap$Country,dfC$COUNTRY)
ix5 = dfC[x5,]
xMap$CODE =ix5$CODE 


df = xMap[,c("Country","Cost","CODE")]
df = df %>%
  group_by(CODE, Country)%>%
  summarise(Amount = sum(Cost))

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

fig <- plot_geo(df)
fig <- fig %>% add_trace(
    z = ~Amount, color = ~Amount, colorscale = 'Viridis',
    text = ~Country, locations = ~CODE
  )
fig <- fig %>% colorbar(title = 'Sales')
fig <- fig %>% layout(
    geo = g
  )

fig
```   

### Sales per Season
    
```{r}
#Amount Realized per season
x1 = x[x$Country == "United Kingdom",]
x2 = x[x$Country == "Netherlands",]
x3 = x[x$Country == "EIRE",]

aX4 = rbind(x1,x2,x3)

tmpS <- x %>%  group_by(seasons) %>% summarize(Amount = mean(Cost))
tmpS$colors <- c("#d35400", "#2980b9", "#2ecc71","#ffd700")
hchart(tmpS, "column", hcaes(x = seasons, y = Amount, color=colors)) %>% 
    hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE)
```


United Kingdom {data-icon="fa-area-chart"}
=====================================  


Column {data-width=450}
-------------------------------------

### Quantity of Goods Sold
```{r}

tmp <- x1 %>% filter(!(seasons=="")) %>% group_by(seasons) %>% tally() %>% mutate(Percent = n/sum(n))
tmp$colors <- c("#d35400", "#2980b9", "#2ecc71","#ffd700")
tmp <- arrange(tmp,desc(Percent))
highchart() %>%
  hc_xAxis(categories = c("Autumn", "Winter", "Summer","Spring")) %>%
  hc_yAxis(title=list(text='Percentage')) %>%
  hc_chart(inverted = TRUE)%>%
  hc_add_series(tmp, "bar", hcaes(x = seasons, y = Percent, color=colors)) %>% 
  hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE) %>% 
  hc_legend(enabled=FALSE)

```

### Rating

```{r}


## Average sentiment
##count of rating
Rating = plyr::count(x1$Sentiment_score)
gg.gauge <- function(pos,breaks=c(0,20,40,60,80,100)) {
  require(ggplot2)
  get.poly <- function(a,b,r1=0.5,r2=1.0) {
    th.start <- pi*(1-a/100)
    th.end   <- pi*(1-b/100)
    th       <- seq(th.start,th.end,length=100)
    x        <- c(r1*cos(th),rev(r2*cos(th)))
    y        <- c(r1*sin(th),rev(r2*sin(th)))
    return(data.frame(x,y))
  }
  ggplot()+ 
    geom_polygon(data=get.poly(breaks[1],breaks[2]),aes(x,y),fill="yellow1")+
    geom_polygon(data=get.poly(breaks[2],breaks[3]),aes(x,y),fill="yellow2")+
    geom_polygon(data=get.poly(breaks[3],breaks[4]),aes(x,y),fill="yellow3")+
    geom_polygon(data=get.poly(breaks[4],breaks[5]),aes(x,y),fill="yellowgreen")+
    geom_polygon(data=get.poly(breaks[5],breaks[6]),aes(x,y),fill="forestgreen")+
    geom_polygon(data=get.poly(pos-1,pos+1,0.2),aes(x,y))+
    geom_text(data=as.data.frame(breaks), size=5, fontface="bold", vjust=0,
              aes(x=1.1*cos(pi*(1-breaks/100)),y=1.1*sin(pi*(1-breaks/100)),label=paste0(breaks,"%")))+
    annotate("text",x=0,y=0,label=paste0(pos,"%"),vjust=0,size=8,fontface="bold")+
    coord_fixed()+
    theme_bw()+
    theme(axis.text=element_blank(),
          axis.title=element_blank(),
          axis.ticks=element_blank(),
          panel.grid=element_blank(),
          panel.border=element_blank()) 
}
gg.gauge(87,breaks=c(0,20,40,60,80,100))

```


    
### Number of Customers per Season by Sales 
    
```{r}

#Number of customers per season with amount realised
# Library
library(fmsb)
#install.packages("fmsb")
 monet = x1 %>%
   group_by(hour,seasons)%>%
   summarise(Amount = sum(Cost))
 
 Aut = monet%>%
      filter(seasons == "Autumn")
Win = monet%>%
      filter(seasons == "Winter")
Sum = monet%>%
      filter(seasons == "Summer")
Spr = monet%>%
      filter(seasons == "Spring")
 
# Create data: note in High school for Jonathan:
monet1 = as.data.frame(matrix( sample(2:20 , 15 , replace=T) , ncol=15))
colnames(monet1) = unique(monet$hour)
monet1[1,] = NA
monet1[2,] = NA
monet1[3,] = NA
monet1[4,] = NA
row.names(monet1) = unique(monet$seasons)
monet1[2,][2:15] = Aut$Amount[1:14] 
monet1[4,][2:15] = Win$Amount[1:14]
monet1[1,][1:15] = Sum$Amount[1:15]
monet1[3,][2:15] = Spr$Amount[1:14]
monet1$`06`[is.na(monet1$`06`)] = 0

# To use the fmsb package, I have to add 2 lines to the dataframe: the max and min of each topic to show on the plot!
monet1 = rbind(rep(500000,15) , rep(0,15) , monet1)
  monet1[c(1,3:6),] = round(monet1[c(1,3:6),]/10000,2)
# Check your data, it has to look like this!
# head(data)

# Color vector
colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )

# plot with default options:
radarchart(monet1  , axistype=1 , 
    #custom polygon
    pcol=colors_border , pfcol=colors_in , plwd=4 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,50,5), cglwd=0.8,
    #custom labels
    vlcex=0.8 
    )
# Add a legend
legend(x=0.7, y=1, legend = rownames(monet1[-c(1,2),]), bty = "n", pch=20 , col=colors_in , text.col = "grey", cex=1.2, pt.cex=3)

```
   
Column {data-width=450}
-------------------------------------

### Probability of Sales per Season 

```{r}
## Probability of sales per season
UKtable = as.data.frame(table(x1$seasons))
UKtable$Prob = UKtable$Freq / sum(UKtable$Freq)
colnames(UKtable) = c("SPS", "Freq", "Prob" )
ggplot(UKtable, aes(x="", y=Prob, fill=SPS)) +
  geom_bar(width = 1, stat = "identity") + coord_polar("y", start=0) 
```

### Top 10 Products Sold

```{r}
## Top 10 products sold
df_order <- x1 %>%
            arrange(desc(Quantity))
df_order = df_order[,3:4]
df_order = df_order[1:12,]
df_order = df_order[-c(4,7),]
df_order$type = c(1:10)
df_order$type = as.factor(df_order$type)


df_order %>%
arrange(desc(Quantity)) %>%
    slice(1:10) %>%
    ggplot(., aes(x=type, y=Quantity, fill = Description))+
              geom_bar(stat='identity')
```


Netherlands {data-icon="fa-area-chart"}
=====================================  

Column {data-width=450}
-------------------------------------

### Quantity of Goods Sold
```{r}

NEtmp <- x2 %>% filter(!(seasons=="")) %>% group_by(seasons) %>% tally() %>% mutate(Percent = n/sum(n))
NEtmp$colors <- c("#d35400", "#2980b9", "#2ecc71","#ffd700")
NEtmp <- arrange(NEtmp,desc(Percent))
highchart() %>%
  hc_xAxis(categories = c("Autumn", "Winter", "Summer","Spring")) %>%
  hc_yAxis(title=list(text='Percentage')) %>%
  hc_chart(inverted = TRUE)%>%
  hc_add_series(NEtmp, "bar", hcaes(x = seasons, y = Percent, color=colors)) %>% 
  hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE) %>% 
  hc_legend(enabled=FALSE)

```

### Rating
```{r}
NERating = plyr::count(x2$Sentiment_score)
gg.gauge(92,breaks=c(0,20,40,60,80,100))

```

    
### Number of Customers per Season by Sales 
    
```{r}

#Number of customers per season with amount realised
# Library
library(fmsb)
#install.packages("fmsb")
 NEmonet = x2 %>%
   group_by(hour,seasons)%>%
   summarise(Amount = sum(Cost))
 
 NAut = NEmonet%>%
      filter(seasons == "Autumn")
NWin = NEmonet%>%
      filter(seasons == "Winter")
NSum = NEmonet%>%
      filter(seasons == "Summer")
NSpr = NEmonet%>%
      filter(seasons == "Spring")
 
# Create data: note in High school for Jonathan:
NEmonet1 = as.data.frame(matrix( sample(2:20 , 15 , replace=T) , ncol=15))
colnames(NEmonet1) = unique(NEmonet$hour)
NEmonet1[1,] = NA
NEmonet1[2,] = NA
NEmonet1[3,] = NA
NEmonet1[4,] = NA
row.names(NEmonet1) = unique(NEmonet$seasons)
NEmonet1[2,][2:11] = NAut$Amount[1:10] 
NEmonet1[4,][3:9] = NWin$Amount[1:7]
NEmonet1[1,][2:11] = NSum$Amount[1:10]
NEmonet1[3,][2:9] = NSpr$Amount[1:8]
NEmonet1$`16`[is.na(NEmonet1$`16`)] = 0
NEmonet1$`17`[is.na(NEmonet1$`17`)] = 0
NEmonet1$`08`[is.na(NEmonet1$`08`)] = 0
NEmonet1[,c(1,12:15)] = NULL

# To use the fmsb package, I have to add 2 lines to the dataframe: the max and min of each topic to show on the plot!
NEmonet1 = rbind(rep(30000,10) , rep(0,10) , NEmonet1)
  NEmonet1[c(1,3:6),] = round(NEmonet1[c(1,3:6),]/1000,2)
# Check your data, it has to look like this!
# head(data)

# Color vector
colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )

# plot with default options:
radarchart(NEmonet1  , axistype=1 , 
    #custom polygon
    pcol=colors_border , pfcol=colors_in , plwd=4 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,30,5), cglwd=0.8,
    #custom labels
    vlcex=0.8 
    )

# Add a legend
legend(x=0.7, y=1, legend = rownames(NEmonet1[-c(1,2),]), bty = "n", pch=20 , col=colors_in , text.col = "grey", cex=1.2, pt.cex=3)
```
   
Column {data-width=450}
-------------------------------------

### Probability of Sales per Season 

```{r}
## Probability of sales per season
NEtable = as.data.frame(table(x2$seasons))
NEtable$Prob = NEtable$Freq / sum(NEtable$Freq)
colnames(NEtable) = c("SPS", "Freq", "Prob" )
ggplot(NEtable, aes(x="", y=Prob, fill=SPS)) +
  geom_bar(width = 1, stat = "identity") + coord_polar("y", start=0)

```

### Top 10 Products Sold

```{r}
NEdf_order <- x2 %>%
            arrange(desc(Quantity))
NEdf_order = NEdf_order[,3:4]
NEdf_order = NEdf_order[1:10,]
NEdf_order$type = c(1:10)
NEdf_order$type = as.factor(NEdf_order$type)
 
NEdf_order %>%
arrange(desc(Quantity)) %>%
    slice(1:10) %>%
    ggplot(., aes(x=type, y=Quantity, fill = Description))+
              geom_bar(stat='identity')
```

Ireland {data-icon="fa-area-chart"}
=====================================  


Column {data-width=450}
-------------------------------------

### Quantity of Goods Sold
```{r}

IRtmp <- x3 %>% filter(!(seasons=="")) %>% group_by(seasons) %>% tally() %>% mutate(Percent = n/sum(n))
IRtmp$colors <- c("#d35400", "#2980b9", "#2ecc71","#ffd700")
IRtmp <- arrange(IRtmp,desc(Percent))
highchart() %>%
  hc_xAxis(categories = c("Autumn", "Winter", "Summer","Spring")) %>%
  hc_yAxis(title=list(text='Percentage')) %>%
  hc_chart(inverted = TRUE)%>%
  hc_add_series(IRtmp, "bar", hcaes(x = seasons, y = Percent, color=colors)) %>% 
  hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE) %>% 
  hc_legend(enabled=FALSE)

```

### Rating

```{r}
## Average sentiment
##count of rating
IRRating = plyr::count(x3$Sentiment_score)
gg.gauge(84,breaks=c(0,20,40,60,80,100))

```

### Number of Customers per Season by Sales 
    
```{r}

#Number of customers per season with amount realised
# Library
library(fmsb)
#install.packages("fmsb")
 IRmonet = x3 %>%
   group_by(hour,seasons)%>%
   summarise(Amount = sum(Cost))
 
 IAut = IRmonet%>%
      filter(seasons == "Autumn")
IWin = IRmonet%>%
      filter(seasons == "Winter")
ISum = IRmonet%>%
      filter(seasons == "Summer")
ISpr = IRmonet%>%
      filter(seasons == "Spring")
 
# Create data: note in High school for Jonathan:
IRmonet1 = as.data.frame(matrix( sample(2:20 , 15 , replace=T) , ncol=15))
colnames(IRmonet1) = unique(IRmonet$hour)
IRmonet1[1,] = NA
IRmonet1[2,] = NA
IRmonet1[3,] = NA
IRmonet1[4,] = NA
row.names(IRmonet1) = unique(IRmonet$seasons)
IRmonet1[1,][1:11] = IAut$Amount[1:11]
IRmonet1[1,][13] = IAut$Amount[12]

IRmonet1[4,][2:11] = IWin$Amount[1:10]
IRmonet1[4,][13] = IWin$Amount[11]

IRmonet1[3,][2:13] = ISum$Amount[1:12]
IRmonet1[2,][1:11] = ISpr$Amount[1:11]
IRmonet1$`07`[is.na(IRmonet1$`07`)] = 0
IRmonet1$`17`[is.na(IRmonet1$`17`)] = 0
IRmonet1$`18`[is.na(IRmonet1$`18`)] = 0
IRmonet1$`19`[is.na(IRmonet1$`19`)] = 0
IRmonet1[,c(14:15)] = NULL

# To use the fmsb package, I have to add 2 lines to the dataframe: the max and min of each topic to show on the plot!
IRmonet1 = rbind(rep(25000,13) , rep(0,13) , IRmonet1)
  IRmonet1[c(1,3:6),] = round(IRmonet1[c(1,3:6),]/100,2)
# Check your data, it has to look like this!
# head(data)

# Color vector
colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )

# plot with default options:
radarchart(IRmonet1  , axistype=1 , 
    #custom polygon
    pcol=colors_border , pfcol=colors_in , plwd=4 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,30,5), cglwd=0.8,
    #custom labels
    vlcex=0.8 
    )

# Add a legend
legend(x=0.7, y=1, legend = rownames(NEmonet1[-c(1,2),]), bty = "n", pch=20 , col=colors_in , text.col = "grey", cex=1.2, pt.cex=3)

```
   
Column {data-width=450}
-------------------------------------

### Probability of Sales per Season 

```{r}
## Probability of sales per season
IRtable = as.data.frame(table(x3$seasons))
IRtable$Prob = IRtable$Freq / sum(IRtable$Freq)
colnames(IRtable) = c("SPS", "Freq", "Prob" )
ggplot(IRtable, aes(x="", y=Prob, fill=SPS)) +
  geom_bar(width = 1, stat = "identity") + coord_polar("y", start=0) 

```

### Top 10 Products Sold

```{r}
## Top 10 products sold
IRdf_order <- x3 %>%
            arrange(desc(Quantity))
IRdf_order = IRdf_order[,3:4]
IRdf_order = IRdf_order[1:10,]
IRdf_order$type = c(1:10)
IRdf_order$type = as.factor(IRdf_order$type)
 
IRdf_order %>%
arrange(desc(Quantity)) %>%
    slice(1:10) %>%
    ggplot(., aes(x=type, y=Quantity, fill = Description))+
              geom_bar(stat='identity')

```


RFM Analysis_1 {data-orientation=rows data-icon="fa-bar-chart"}
=====================================

## Row 1 {data-height=300}  

### Top 7 Customers
```{r}
#segment by country
library(reshape2)
library(knitr)
SBC = df_RFM %>%
  group_by(Country,segmentRFM) %>%
  summarise(Length = length(segmentRFM))

df_SBC = dcast(SBC,Country~segmentRFM)

df_SBC[is.na(df_SBC)] = 0

df_SBC = df_SBC[order(df_SBC$Champions, decreasing = TRUE),]  

kable(head(df_SBC),row.names = FALSE)
```

## Row 2 {data-height=300}

### Bottom 6 customers
```{r}
kable(tail (df_SBC),row.names = FALSE)
```

RFM Analysis_2 {data-orientation=rows data-icon="fa-bar-chart"}
=====================================

Column {data-width=450}
-------------------------------------

### Number of Customers per Segment

```{r}
df_TNC = SBC %>%
  group_by(segmentRFM)%>%
  summarise(TNC = sum(Length))%>%
  mutate(Percent = TNC/sum(TNC))
  

df_TNC$colors <- c("#d35400", "#2980b9", "#2ecc71","#ffd700","#4682B4","#AF46B4","#B47846","#4BB446")
df_TNC <- arrange(df_TNC,desc(Percent))
library(highcharter)
highchart() %>%
  hc_xAxis(categories = df_TNC$segmentRFM) %>%
  hc_yAxis(title=list(text='Percentage')) %>%
   hc_chart(inverted = TRUE)%>%
  hc_add_series(df_TNC, "bar", hcaes(x = segmentRFM, y = Percent, color=colors)) %>% 
  hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE) %>% 
  hc_legend(enabled=FALSE)

```

### Cluster Plot

```{r}
library(cluster)    # clustering algorithms
library(factoextra)
library(tidyverse)

ClusterA = df_RFM[,1:4]
set.seed(200)
clusters <- kmeans(ClusterA, 3, nstart = 10) 
fviz_cluster(clusters,ClusterA)

```

### Cluster Interpretation
```{r}
ClusterA1 = as.data.frame(ClusterA[clusters$cluster == 1,])
ClusterA2 = as.data.frame(ClusterA[clusters$cluster == 2,])
ClusterA3 = as.data.frame(ClusterA[clusters$cluster == 3,])

#investigate what each cluster represent
ClusterA1_I = ClusterA1%>%
  summarize(Customers = n_distinct(CustomerID), Rmean = round (mean(Recency),0), Fmean = round(mean(Frequency),0),Mmean = round(mean(Monetary_Value),0),Revenue = round(sum(Monetary_Value),0))

ClusterA2_I = ClusterA2%>%
  summarize(Customers = n_distinct(CustomerID),Rmean = round (mean(Recency),0), Fmean = round(mean(Frequency),0),Mmean = round(mean(Monetary_Value),0),Revenue = round(sum(Monetary_Value),0))

ClusterA3_I = ClusterA3%>%
  summarize(Customers = n_distinct(CustomerID),Rmean = round (mean(Recency),0), Fmean = round(mean(Frequency),0),Mmean = round(mean(Monetary_Value),0),Revenue = round(sum(Monetary_Value),0))

  
#put together in a table
ClusterA_I = rbind(ClusterA1_I,ClusterA2_I,ClusterA3_I)
 ClusterA_I$Int_Clust = c("Medium_Value","Low_Value","High_Value") 
ClusterA_I$colors <- c("#d35400","#008000","#0000FF")
ClusterA_I <- arrange(ClusterA_I,desc(Customers))
library(highcharter)
highchart() %>%
  hc_xAxis(categories = ClusterA_I$Int_Clust) %>%
  hc_yAxis(title=list(text='Number of Customers')) %>%
   hc_chart(inverted = TRUE)%>%
  hc_add_series(ClusterA_I, "column", hcaes(x = Int_Clust, y = Customers, color=colors)) %>% 
  hc_tooltip(pointFormat = "{point.y:.2f}</br>",shared = FALSE) %>% 
  hc_legend(enabled=FALSE)


```


Forecasting {data-orientation=rows data-icon="fa-bar-chart"}
=====================================

## Row 1 {data-height=500}
### Three months Forecast 
```{r}
library(prophet)
library(shiny)
library(plotly)

df = x1[,c("InvoiceDate","Cost")]   
colnames(df) = c("ds","y")

df$ds = as.Date(df$ds)
df = df %>%
  group_by(ds) %>%
  summarise(y = sum(y))

# Create a prophet object
m <- prophet(df, daily.seasonality = TRUE) 

# Extend dataframe 120 days into the future
future <- make_future_dataframe(m, periods = 120)

# Generate forecast for next 120 days
forecast <- predict(m, future)

#plot(m,forecast,xlab = "Date", ylab ="Sales")
dyplot.prophet(m,forecast)

```

